A dataset of Scratch programs,\\Scraped, Shaped and Scored

### 2017-02-17 MSR-Scratch.tex
Updates footnotes with temp dataset repository location

The goal of this paper is to present an open and timely dataset of recent Scratch programs, along with their metadata, that can facilitate quantitative research in the fields of source code analysis and computing education.
The dataset contains 250 thousand Scratch projects, from more than 100 thousand different users, that were scraped from the Scratch project repository.
It is made available as a database\footnote{{\fenia{add anonymized address, update it in repo footnote}}} which includes, for each Scratch project, its metadata and the program data, along with programming mastery scoring results from the Dr. Scratch quality assessment tool \cite{moreno_automatic_2014}.

@@

We ran Kragle on March 2nd 2016 for 24 hours and, during that time, it obtained the JSON code for \nPrograms projects. Out of those, we failed to parse and further analyze 2,367 projects due to technical difficulties with the JSON files.
Kragle, as well as all scraped projects and our analysis files are available.\footnote{\label{repo}\url{https://github.com/TUDelftScratchLab/ScratchDataset}}

@@

The dataset contains 250 thousand Scratch projects, from more than 100 thousand different users, that were scraped from the Scratch project repository.
It is made available as a database\footnote{{\fenia{add anonymized address, update it in repo footnote}}} which includes the source code of the Scratch projects, their metadata, and their programming mastery scoring results.

>>>>

The goal of this paper is to present an open and timely dataset of recent Scratch programs, along with their metadata, that can facilitate quantitative research in the fields of source code analysis and computing education.
The dataset contains 250 thousand Scratch projects, from more than 100 thousand different users, that were scraped from the Scratch project repository.
It is made available as a database\footnote{\label{dataseturl}The temporary location of the dataset, for the purpose of the review, is \url{https://github.com/scratchmsrds/scratchmrsds}} which includes, for each Scratch project, its metadata and the program data, along with programming mastery scoring results from the Dr. Scratch quality assessment tool \cite{moreno_automatic_2014}.

@@

We ran Kragle on March 2nd 2016 for 24 hours and, during that time, it obtained the JSON code for \nPrograms projects. Out of those, we failed to parse and further analyze 2,367 projects due to technical difficulties with the JSON files.
Kragle, as well as all scraped projects and our analysis files are available.\footnotemark[\ref{dataseturl}]

@@

The dataset contains 250 thousand Scratch projects, from more than 100 thousand different users, that were scraped from the Scratch project repository.
It is made available as a database\footnotemark[\ref{dataseturl}] which includes the source code of the Scratch projects, their metadata, and their programming mastery scoring results.
